Shift-sensitive Power Transformations for Transforming Data to Normality

### 2023-02-10 manuscript/manuscript.Rmd
Update to manuscript.

---
title: "Shift-sensitive Power Transformations for Transforming Data to Normality"
author: "Alex Zwanenburg"
date: "2023-01-06"
output: 
  pdf_document:
    latex_engine: lualatex
bibliography: "refs.bib"
header-includes:
   - \usepackage{amsmath}
   - \usepackage{booktabs}
   - \DeclareMathOperator*{\argmax}{argmax}
   - \DeclareMathOperator*{\argmin}{argmin}
   - \DeclareMathOperator{\sgn}{sgn}
---

@@

.compute_lambda <- function(x){
  # Create transformer object.
  transformer <- suppressWarnings(
    power.transform::find_transformation_parameters(
      x = x,
      method = "yeo_johnson",
      robust = FALSE,
      shift = TRUE))

@@

# Compute lambda values without weighting for Yeo-Johnson.
target_lambda <- sapply(
  x,
  .compute_lambda)

@@

# Find optimised k1 and k2 values for all combinations of weight sources and
# weighting functions.
x <- mapply(
  function(x, n, alpha, beta, target_lambda, outlier_fraction){

    parameters <- list("n" = n, "alpha"=alpha, "beta" = beta, "target_lambda"=target_lambda)

@@

    return(x)
  },
  x = x,
  n = n,
  alpha = alpha,
  beta = beta,
  target_lambda = target_lambda,
  MoreArgs=list("outlier_fraction"=outlier_fraction),
  SIMPLIFY=FALSE,
  USE.NAMES=FALSE)

@@

    # Non-robust transformation.
    fun_args <- list(
      "method" = "yeo_johnson",
      "robust" = FALSE,
      "shift" = TRUE)

@@

    yield(list(
      "name" = "non-robust",
      "fun_args" = fun_args,
      "opt_args" = opt_args
    ))

@@

        def_opt_init <- list("k1" = 0.8, "k2" = 0.95)

      } else if(robustness_source == "transformed"){
        def_opt_init <- list("k1" = 1.5, "k2" = 3.0)

      } else if(robustness_source == "residual"){
        def_opt_init <- list("k1" = 0.15, "k2" = 1.0)
      }

      for(robustness_weighting_function in c("step", "triangle", "cosine")){

        fun_args <- list(
          "method" = "yeo_johnson",
          "robust" = TRUE,
          "shift" = TRUE,
          "weight_method" = paste0(robustness_source, "_", robustness_weighting_function),
          "backup_use_default" = FALSE)

@@

        yield(list(
          "name" = paste0(robustness_source, "-", robustness_weighting_function),
          "fun_args" = fun_args,
          "opt_args" = list("initial" = opt_init, "limits" = opt_limits)
        ))
      }
    }
  })

# Function for computing transformer parameters under optimisation constraints.
compute_robust_lambda <- function(
    x,
    fun_args,
    opt_args,
    cl=NULL){

@@

    parameter_data <- c(
      x$parameters,
      opt_args,
      list(
        "weight_method" = fun_args$weight_method,
        "lambda" = transformer@lambda,
        "shift" = transformer@shift)
    )

@@

  if(is.null(cl)){
    parameter_data <- lapply(
      x,
      ..outlier_parser,
      fun_args = fun_args,
      opt_args = opt_args)

  } else {
    parameter_data <- parallel::parLapply(
      cl = cl,
      X = x,
      fun = ..outlier_parser,
      fun_args = fun_args,
      opt_args = opt_args)
  }

@@

# Inner optimisation function that sets the loss.
..optimisation_function <- function(
  opt_param,
  x,
  fun_args,
  cl = NULL){

@@

  parameter_data <- compute_robust_lambda(
    x = x,
    fun_args = fun_args,
    opt_args = opt_args,
    cl = cl)

  lambda_error <- sapply(
    parameter_data,
    function(x) (abs(x$lambda - x$target_lambda)))

@@

# Outer optimisation function
.optimisation_function <- function(
    experiment,
    x,
    cl = NULL){

@@

    h <- nloptr::sbplx(
      x0 = x0,
      fn = ..optimisation_function,
      lower = lower,
      upper = upper,
      control=list("xtol_rel"=1e-3, "ftol_rel"=1e-4),
      x = x,
      fun_args = experiment$fun_args,
      cl = cl)

    if(length(h$par) == 1){
      return(list("name"=experiment$name, "k1" = h$par, "value" = h$value))

    } else {
      return(list("name"=experiment$name, "k1" = h$par[1], "k2" = h$par[2], "value" = h$value))
    }

  } else {
    value <- ..optimisation_function(
      opt_param=list(),
      x = x,
      fun_args=experiment$fun_args,
      cl = cl)

    return(list("name"=experiment$name, "value" = value))
  }
}

# Start cluster
cl <- parallel::makeCluster(8L)

experiment_results <- lapply(
  coro::collect(experiment_args()),
  .optimisation_function,
  x = x,
  cl = cl)

@@

```{=latex}
\begin{table}
\begin{center}
\caption{Optimal weighting parameters and corresponding loss. $p^{*}$ indicates use of the empirical distribution of feature values, $z$ the z-score of the transformed feature values, and $r$ the residual error between the z-score of transformed feature values and the expected z-score according to the normal distribution. The \textit{initial} column shows the starting parameter value for the optimisation process, with the corresponding boundary values in the \textit{limits} column. The {optimal} column shows the optimal parameter values. The \textit{loss} column shows the loss achieved by each method, under optimised parameters. Lower loss indicates better robustness against outliers.}
\begin{tabular}{l r r r r r r r}

@@

\midrule
non-robust               & ---  & ---       & ---  & ---  & ---       & ---   & 225 \\
$p^{*}$ (step)           & 0.80 & $(0, 1]$  & 0.92 & ---  & ---       & ---   & 125 \\
$p^{*}$ (triangle)       & 0.80 & $(0, 1]$  & 0.88 & 0.95 & $(0, 1]$  & 0.93  & 126 \\
$p^{*}$ (tapered cosine) & 0.80 & $(0, 1]$  & 0.89 & 0.95 & $(0, 1]$  & 0.93  & 124 \\
$z$ (step)               & 1.50 & $(0, 10]$ & 1.03 & ---  & ---       & ---   & 331 \\
$z$ (triangle)           & 1.50 & $(0, 10]$ & 2.79 & 3.00 & $(0, 10]$ & 4.12  & 768 \\
$z$ (tapered cosine)     & 1.50 & $(0, 10]$ & 2.69 & 3.00 & $(0, 10]$ & 4.21  & 772 \\
$r$ (step)               & 0.15 & $(0, 10]$ & 0.05 & ---  & ---       & ---   & 1957 \\
$r$ (triangle)           & 0.15 & $(0, 10]$ & 9.96 & 1.00 & $(0, 10]$ & 10.00 & 483 \\
$r$ (tapered cosine)     & 0.15 & $(0, 10]$ & 9.97 & 1.00 & $(0, 10]$ & 10.00 & 484 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}
```

@@

            #for(method in c("box_cox", "yeo_johnson")){
            for(method in c("yeo_johnson")){
              for(weight_method in c("none", "original_step", "original_cosine", "transformed_step", "transformed_cosine", "residual_step", "residual_cosine")){

@@

                # Optimal parameter values from the previous experiment.
                if(weight_method == "original_step"){
                  k1 <- 0.92

                } else if(weight_method == "original_cosine"){
                  k1 <- 0.89
                  k2 <- 0.93

                } else if(weight_method == "transformed_step"){
                  k1 <- 1.03

                } else if(weight_method == "transformed_cosine"){
                  k1 <- 2.69
                  k2 <- 4.21

                } else if(weight_method == "residual_step"){
                  k1 <- 0.05

                } else if(weight_method == "residual_cosine"){
                  k1 <- 9.97
                  k2 <- 10.0
                }

@@

@@

# Update distribution, method and version to factors.
data$distribution <- factor(
  x = data$distribution,
  levels = c("normal", "right-skewed", "left-skewed"))
data$method <- factor(
  x = data$method,
  levels = c("yeo_johnson"),
  labels = c("Yeo-Johnson"))
data$weight_method <- factor(
  x = data$weight_method,
  levels = c("none", "original_step", "original_cosine", "transformed_step", "transformed_cosine", "residual_step", "residual_cosine"),
  labels = c("non-robust", "emp. prob. (step)", "emp. prob. (tap. cos.)", "z-score (step)", "z-score (tap. cos.)", "residual (step)", "residual (tap. cos.)"))

@@

#### Normal distribution -------------------------------------------------------
p_normal_t <- .create_outlier_fraction_plot(
  data = data[distribution == "normal" & weight_method %in% top_group],
  plot_theme = plot_theme,
  limits = top_limits,
  lambda_target = data[distribution == "normal" & weight_method == "non-robust" & k == 0.0]$mean_lambda)
p_normal_t <- p_normal_t + ggplot2::ggtitle(label="normal distribution")
p_normal_t <- p_normal_t + ggplot2::theme(
  axis.title.x = ggplot2::element_blank(),
  axis.text.x = ggplot2::element_blank())

@@

#### Right skewed distribution -------------------------------------------------
p_right_t <- .create_outlier_fraction_plot(
  data = data[distribution == "right-skewed" & weight_method %in% top_group],
  plot_theme = plot_theme,
  limits= top_limits,
  lambda_target = data[distribution == "right-skewed" & weight_method == "non-robust" & k == 0.0]$mean_lambda)
p_right_t <- p_right_t + ggplot2::ggtitle(label="right-skewed distribution")
p_right_t <- p_right_t + ggplot2::theme(
  axis.title.x = ggplot2::element_blank(),
  axis.text.x = ggplot2::element_blank(),
  axis.title.y = ggplot2::element_blank(),
  axis.text.y = ggplot2::element_blank())

@@

#### Left skewed distribution --------------------------------------------------
p_left_t <- .create_outlier_fraction_plot(
  data = data[distribution == "left-skewed" & weight_method %in% top_group],
  plot_theme = plot_theme,
  limits = top_limits,
  lambda_target = data[distribution == "left-skewed" & weight_method == "non-robust" & k == 0.0]$mean_lambda,
  guide = TRUE)
p_left_t <- p_left_t + ggplot2::ggtitle(label="left-skewed distribution")
p_left_t <- p_left_t + ggplot2::theme(
  axis.title.x = ggplot2::element_blank(),
  axis.text.x = ggplot2::element_blank(),
  axis.title.y = ggplot2::element_blank(),
  axis.text.y = ggplot2::element_blank())

@@

@@

>>>>

---
title: "Shift-sensitive Power Transformations for Transforming Data to Normality"
author: "Alex Zwanenburg"
date: "2023-01-06"
output:
  pdf_document:
    latex_engine: lualatex
bibliography: refs.bib
header-includes:
- \usepackage{amsmath}
- \usepackage{booktabs}
- \DeclareMathOperator*{\argmax}{argmax}
- \DeclareMathOperator*{\argmin}{argmin}
- \DeclareMathOperator{\sgn}{sgn}
---

@@

.compute_lambda <- function(x, method){
  # Create transformer object.
  transformer <- suppressWarnings(
    power.transform::find_transformation_parameters(
      x = x,
      method = method,
      robust = FALSE,
      shift = TRUE))

@@

# Compute lambda values without weighting for Box-Cox.
target_lambda_bc <- sapply(
  x,
  .compute_lambda,
  method = "box_cox")

# Compute lambda values without weighting for Yeo-Johnson
target_lambda_yj <- sapply(
  x,
  .compute_lambda,
  method = "yeo_johnson")

@@

# Find optimised k1 and k2 values for all combinations of weight sources and
# weighting functions.
x <- mapply(
  function(x, n, alpha, beta, target_lambda_bc, target_lambda_yj, outlier_fraction){

    parameters <- list("n" = n, "alpha"=alpha, "beta" = beta, "target_lambda_bc"=target_lambda_bc, "target_lambda_yj"=target_lambda_yj)

@@

    return(x)
  },
  x = x,
  n = n,
  alpha = alpha,
  beta = beta,
  target_lambda_bc = target_lambda_bc,
  target_lambda_yj = target_lambda_yj,
  MoreArgs=list("outlier_fraction"=outlier_fraction),
  SIMPLIFY=FALSE,
  USE.NAMES=FALSE)

@@

    for(method in c("box_cox", "yeo_johnson")){
      # Non-robust transformation.
      fun_args <- list(
        "method" = method,
        "robust" = FALSE,
        "shift" = TRUE)

@@

      yield(list(
        "name" = "non-robust",
        "method" = method,
        "fun_args" = fun_args,
        "opt_args" = opt_args
      ))
    }

@@

        def_opt_init <- list("k1" = 0.80, "k2" = 0.95)

      } else if(robustness_source == "transformed"){
        def_opt_init <- list("k1" = 1.28, "k2" = 1.96)

      } else if(robustness_source == "residual"){
        def_opt_init <- list("k1" = 0.50, "k2" = 1.0)
      }

      for(method in c("box_cox", "yeo_johnson")){
        for(robustness_weighting_function in c("step", "triangle", "cosine")){

          fun_args <- list(
            "method" = method,
            "robust" = TRUE,
            "shift" = TRUE,
            "weight_method" = paste0(robustness_source, "_", robustness_weighting_function),
            "backup_use_default" = FALSE)

@@

          yield(list(
            "name" = paste0(robustness_source, "-", robustness_weighting_function),
            "method" = method,
            "fun_args" = fun_args,
            "opt_args" = list("initial" = opt_init, "limits" = opt_limits)
          ))
        }
      }
    }
  })

# Function for computing transformer parameters under optimisation constraints.
compute_robust_lambda <- function(
    x,
    fun_args,
    opt_args,
    cl_internal=NULL){

@@

    parameter_data <- c(
      x$parameters,
      opt_args,
      list(
        "method" = fun_args$method,
        "weight_method" = fun_args$weight_method,
        "lambda" = transformer@lambda,
        "shift" = transformer@shift)
    )

@@

  if(is.null(cl_internal)){
    parameter_data <- lapply(
      x,
      ..outlier_parser,
      fun_args = fun_args,
      opt_args = opt_args)

  } else {
    parameter_data <- parallel::parLapply(
      cl = cl_internal,
      X = x,
      fun = ..outlier_parser,
      fun_args = fun_args,
      opt_args = opt_args)
  }

@@

# Inner optimisation function that sets the loss.
..optimisation_function <- function(
  opt_param,
  x,
  fun_args,
  cl_internal = NULL){

@@

  parameter_data <- compute_robust_lambda(
    x = x,
    fun_args = fun_args,
    opt_args = opt_args,
    cl_internal = cl_internal)

  if(fun_args$method == "box_cox"){
    lambda_error <- sapply(
      parameter_data,
      function(x) (abs(x$lambda - x$target_lambda_bc)))

  } else {
    # Yeo-Johnson.
    lambda_error <- sapply(
      parameter_data,
      function(x) (abs(x$lambda - x$target_lambda_yj)))
  }

@@

# Outer optimisation function
.optimisation_function <- function(
    experiment,
    data,
    cl_internal = NULL){

  set.seed(9)

@@

    h <- nloptr::sbplx(
      x0 = x0,
      fn = ..optimisation_function,
      lower = lower,
      upper = upper,
      control=list("xtol_rel"=1e-3, "ftol_rel"=1e-4),
      x = data,
      fun_args = experiment$fun_args,
      cl_internal = cl_internal)

    if(length(h$par) == 1){
      return(list("name"=experiment$name, "method"=experiment$method, "k1" = h$par, "value" = h$value))

    } else {
      return(list("name"=experiment$name, "method"=experiment$method, "k1" = h$par[1], "k2" = h$par[2], "value" = h$value))
    }

  } else {
    value <- ..optimisation_function(
      opt_param=list(),
      x = data,
      fun_args=experiment$fun_args,
      cl = cl_internal)

    return(list("name"=experiment$name, "method"=experiment$method, "value" = value))
  }
}

# Start cluster
cl <- parallel::makeCluster(18L)

parallel::clusterExport(
  cl=cl,
  varlist = c("compute_robust_lambda", "..optimisation_function")
)

experiment_results <- parallel::parLapplyLB(
  cl = cl,
  X = coro::collect(experiment_args()),
  fun = .optimisation_function,
  data = x,
  chunk.size = 1L)

@@

```{=latex}
\begin{table}
\begin{center}
\caption{Optimal weighting parameters and corresponding loss for \textbf{shift-sensitive Box-Cox} power transformations. $p^{*}$ indicates use of the empirical distribution of feature values, $z$ the z-score of the transformed feature values, and $r$ the residual error between the z-score of transformed feature values and the expected z-score according to the normal distribution. The \textit{initial} column shows the starting parameter value for the optimisation process, with the corresponding boundary values in the \textit{limits} column. The {optimal} column shows the optimal parameter values. The \textit{loss} column shows the loss achieved by each method, under optimised parameters. Lower loss indicates better robustness against outliers.}
\begin{tabular}{l r r r r r r r}

@@

\midrule
non-robust               & ---  & ---       & ---  & ---  & ---       & ---  & 783 \\
$p^{*}$ (step)           & 0.80 & $(0, 1]$  & 0.84 & ---  & ---       & ---  & 587 \\
$p^{*}$ (triangle)       & 0.80 & $(0, 1]$  & 0.78 & 0.95 & $(0, 1]$  & 0.99 & 587 \\
$p^{*}$ (tapered cosine) & 0.80 & $(0, 1]$  & 0.76 & 0.95 & $(0, 1]$  & 0.98 & 583 \\
$z$ (step)               & 1.28 & $(0, 10]$ & 1.09 & ---  & ---       & ---  & 1135 \\
$z$ (triangle)           & 1.28 & $(0, 10]$ & 0.26 & 1.96 & $(0, 10]$ & 5.47 & 1813 \\
$z$ (tapered cosine)     & 1.28 & $(0, 10]$ & 0.03 & 1.96 & $(0, 10]$ & 6.91 & 1844 \\
$r$ (step)               & 0.50 & $(0, 10]$ & 1.56 & ---  & ---       & ---  & 1837 \\
$r$ (triangle)           & 0.50 & $(0, 10]$ & 1.49 & 1.00 & $(0, 10]$ & 1.51 & 1877 \\
$r$ (tapered cosine)     & 0.50 & $(0, 10]$ & 1.32 & 1.00 & $(0, 10]$ & 1.65 & 1834 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}
```

```{=latex}
\begin{table}
\begin{center}
\caption{Optimal weighting parameters and corresponding loss for \textbf{shift-sensitive Yeo-Johnson} power transformations. $p^{*}$ indicates use of the empirical distribution of feature values, $z$ the z-score of the transformed feature values, and $r$ the residual error between the z-score of transformed feature values and the expected z-score according to the normal distribution. The \textit{initial} column shows the starting parameter value for the optimisation process, with the corresponding boundary values in the \textit{limits} column. The {optimal} column shows the optimal parameter values. The \textit{loss} column shows the loss achieved by each method, under optimised parameters. Lower loss indicates better robustness against outliers.}
\begin{tabular}{l r r r r r r r}

\midrule
non-robust               & ---  & ---       & ---   & ---  & ---       & ---   & 225 \\
$p^{*}$ (step)           & 0.80 & $(0, 1]$  & 0.92  & ---  & ---       & ---   & 125 \\
$p^{*}$ (triangle)       & 0.80 & $(0, 1]$  & 0.88  & 0.95 & $(0, 1]$  & 0.93  & 126 \\
$p^{*}$ (tapered cosine) & 0.80 & $(0, 1]$  & 0.89  & 0.95 & $(0, 1]$  & 0.93  & 124 \\
$z$ (step)               & 1.28 & $(0, 10]$ & 1.04  & ---  & ---       & ---   & 333 \\
$z$ (triangle)           & 1.28 & $(0, 10]$ & 0.12  & 1.96 & $(0, 10]$ & 9.91  & 620 \\
$z$ (tapered cosine)     & 1.28 & $(0, 10]$ & 0.23  & 1.96 & $(0, 10]$ & 5.63  & 716 \\
$r$ (step)               & 0.50 & $(0, 10]$ & 10.00 & ---  & ---       & ---   & 485 \\
$r$ (triangle)           & 0.50 & $(0, 10]$ & 9.96  & 1.00 & $(0, 10]$ & 10.00 & 483 \\
$r$ (tapered cosine)     & 0.50 & $(0, 10]$ & 9.97  & 1.00 & $(0, 10]$ & 10.00 & 484 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}
```

@@

            for(method in c("box_cox", "yeo_johnson")){
              for(weight_method in c("none", "original_step", "original_cosine", "transformed_step", "transformed_cosine", "residual_step", "residual_cosine")){

@@

                # Optimal parameter values from the previous experiment.
                if(weight_method == "original_step"){
                  k1 <- ifelse(method == "box_cox", 0.84, 0.92)

                } else if(weight_method == "original_cosine"){
                  k1 <- ifelse(method == "box_cox", 0.76, 0.89)
                  k2 <- ifelse(method == "box_cox", 0.98, 0.93)

                } else if(weight_method == "transformed_step"){
                  k1 <- ifelse(method == "box_cox", 1.09, 1.04)

                } else if(weight_method == "transformed_cosine"){
                  k1 <- ifelse(method == "box_cox", 0.03, 0.12)
                  k2 <- ifelse(method == "box_cox", 6.91, 5.63)

                } else if(weight_method == "residual_step"){
                  k1 <- ifelse(method == "box_cox", 1.56, 10.00)

                } else if(weight_method == "residual_cosine"){
                  k1 <- ifelse(method == "box_cox", 1.32, 9.97)
                  k2 <- ifelse(method == "box_cox", 1.65, 10.0)
                }

@@

  # Computations ---------------------------------------------------------------

@@

# Update distribution, method and version to factors.
data$distribution <- factor(
  x = data$distribution,
  levels = c("normal", "right-skewed", "left-skewed"))
data$method <- factor(
  x = data$method,
  levels = c("box_cox", "yeo_johnson"),
  labels = c("Box-Cox", "Yeo-Johnson"))
data$weight_method <- factor(
  x = data$weight_method,
  levels = c("none", "original_step", "original_cosine", "transformed_step", "transformed_cosine", "residual_step", "residual_cosine"),
  labels = c("non-robust", "emp. prob. (step)", "emp. prob. (tap. cos.)", "z-score (step)", "z-score (tap. cos.)", "residual (step)", "residual (tap. cos.)"))

@@

# Normal distribution ----------------------------------------------------------
p_normal_t <- .create_outlier_fraction_plot(
  data = data[distribution == "normal" & weight_method %in% top_group],
  plot_theme = plot_theme,
  limits = top_limits,
  lambda_target = data[distribution == "normal" & weight_method == "non-robust" & k == 0.0]$mean_lambda)
p_normal_t <- p_normal_t + ggplot2::ggtitle(label="normal distribution")
p_normal_t <- p_normal_t + ggplot2::theme(
  axis.title.x = ggplot2::element_blank(),
  axis.text.x = ggplot2::element_blank())

@@

# Right skewed distribution ----------------------------------------------------
p_right_t <- .create_outlier_fraction_plot(
  data = data[distribution == "right-skewed" & weight_method %in% top_group],
  plot_theme = plot_theme,
  limits= top_limits,
  lambda_target = data[distribution == "right-skewed" & weight_method == "non-robust" & k == 0.0]$mean_lambda)
p_right_t <- p_right_t + ggplot2::ggtitle(label="right-skewed distribution")
p_right_t <- p_right_t + ggplot2::theme(
  axis.title.x = ggplot2::element_blank(),
  axis.text.x = ggplot2::element_blank(),
  axis.title.y = ggplot2::element_blank(),
  axis.text.y = ggplot2::element_blank())

@@

# Left skewed distribution -----------------------------------------------------
p_left_t <- .create_outlier_fraction_plot(
  data = data[distribution == "left-skewed" & weight_method %in% top_group],
  plot_theme = plot_theme,
  limits = top_limits,
  lambda_target = data[distribution == "left-skewed" & weight_method == "non-robust" & k == 0.0]$mean_lambda,
  guide = TRUE)
p_left_t <- p_left_t + ggplot2::ggtitle(label="left-skewed distribution")
p_left_t <- p_left_t + ggplot2::theme(
  axis.title.x = ggplot2::element_blank(),
  axis.text.x = ggplot2::element_blank(),
  axis.title.y = ggplot2::element_blank(),
  axis.text.y = ggplot2::element_blank())

@@

# Aggregate --------------------------------------------------------------------

@@

## Empirical goodness of fit test

To answer:
 1. What is the residual threshold and the volume required to avoid rejecting transformations? Optimise: 1. window; 2. threshold; 3. threshold fraction. ? Create a figure that summarises residual error thresholds (50%, 80%, 90%, 95%, 99%, 100%), below which x% of the data falls.
 2. How does this correspond to distance between bimodal normal distributions?

```{r goodness-of-fit, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "CHECK. ")

residual <- residual_error <- threshold <- NULL

x <- mapply(
  function(x, n, alpha, beta, outlier_fraction){

    parameters <- list("n" = n, "alpha"=alpha, "beta" = beta)

    return(x)
  },
  x = x,
  n = n,
  alpha = alpha,
  beta = beta,
  MoreArgs=list("outlier_fraction"=outlier_fraction),
  SIMPLIFY=FALSE,
  USE.NAMES=FALSE)

x <- unlist(x, recursive = FALSE)
x <- lapply(seq_along(x), function(ii, x){
  x$distribution_id <- ii

  return(x)
})

compute_residuals <- function(
    x,
    n_sample = 200){

  # Set interpolation points.
  p_sample <- (seq_len(n_sample) - 1/3) / (n_sample + 1/3)

  # Determine residuals for Box-Cox transformations.
  transformer_bc <- suppressWarnings(power.transform::find_transformation_parameters(
    method = "box_cox",
    shift = TRUE,
    robust = TRUE,
    weight_method = "original_cosine",
    k1 = 0.89,
    k2 = 0.93))

  residual_data <- power.transform::get_residuals(x = x$x, transformer = transformer_bc)

  residual <- stats::approx(
    x = residual_data$p,
    y = abs(residual_data$residual),
    xout = p_sample,
    rule = 2,
    ties = max)

  residual_bc <- data.table::data.table(
    "distribution_id" = x$distribution_id,
    "p" = p_sample,
    "residual" = residual,
    "method" = "box_cox")

  # Determine residuals for Yeo-Johnson transformations.
  transformer_yj <- suppressWarnings(power.transform::find_transformation_parameters(
    method = "yeo_johnson",
    shift = TRUE,
    robust = TRUE,
    weight_method = "original_cosine",
    k1 = 0.89,
    k2 = 0.93))

  residual_data <- power.transform::get_residuals(x = x$x, transformer = transformer_yj)

  residual <- stats::approx(
    x = residual_data$p,
    y = abs(residual_data$residual),
    xout = p_sample,
    rule = 2,
    ties = max)

  residual_yj <- data.table::data.table(
    "distribution_id" = x$distribution_id,
    "p" = p_sample,
    "residual" = residual,
    "method" = "yeo_johnson")

  return(data.table::rbindlist(list(residual_bc, residual_yj)))
}

data <- lapply(
  x,
  compute_residuals)

data <- data.table::rbindlist(data)

saveRDS(
  object=data,
  file=file.path(manuscript_dir, "residual_plot.RDS"))

data <- data[, list(
  "residual_50"=stats::quantile(residual, probs=0.50),
  "residual_90"=stats::quantile(residual, probs=0.90),
  "residual_95"=stats::quantile(residual, probs=0.95),
  "residual_99"=stats::quantile(residual, probs=0.99),
  "residual_max"=max(residual)),
  by=c("p", "method")]

data <- data.table::melt(
  data = data,
  id.vars = c("p", "method"),
  variable.name = "threshold",
  value.name = "residual_error")

data$threshold <- factor(
  x = data$threshold,
  levels = c("residual_50", "residual_90", "residual_95", "residual_99", "residual_max"),
  labels = c("50 %", "90 %", "95 %", "99 %", "100 %"))

data$method <- factor(
  x = data$method,
  levels = c("box_cox", "yeo_johnson"),
  labels = c("Box-Cox", "Yeo-Johnson"))

p_bc <- ggplot2::ggplot(
  data = data[method == "Box-Cox"],
  mapping = ggplot2::aes(
    x = p,
    y = residual_error,
    colour = threshold))
p_bc <- p_bc + plot_theme
p_bc <- p_bc + ggplot2::geom_line()
p_bc <- p_bc + ggplot2::scale_colour_discrete(
  name = "Box-Cox threshold",
  type=list("50 %" = "#ABC6E2", "90 %" = "#779EC6", "95 %" = "#4E79A7", "99 %" = "#346394", "100 %" = "#1D4D7E"))
p_bc <- p_bc <- ggplot2::xlab("empirical probability")

p_yj <- ggplot2::ggplot(
  data = data[method == "Yeo-Johnson"],
  mapping = ggplot2::aes(
    x = p,
    y = residual_error,
    colour = threshold))
p_yj <- p_yj + plot_theme
p_yj <- p_yj + ggplot2::geom_line()
p_yj <- p_yj + ggplot2::scale_colour_discrete(
  name = "Yeo-Johnson threshold",
  type=list("50 %" = "#FFBD7D", "90 %" = "#FFA954", "95 %" = "#F28E2B", "99 %" = "#CD6B0B", "100 %" = "#A25000"))
p_yj <- p_yj <- ggplot2::xlab("empirical probability")
